---
title: "Cleaning excel file"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Load libraries

First, we load required libraries for importing and data cleaning
```{r}
library(readxl)
library(tidyverse)
library(openxlsx)
library(dplyr)
library(here)
library(janitor)
library(skimr)
library(stringr)
library(ggplot2)
```

# Import file from excel file 

We import two sheets from excel file. Sheet 8.Effects, and sheet 7. Evaluations.

```{r}
ruta_file <- here("data", "effect-sizes-raw.xlsx")
effects <- read_excel(ruta_file, sheet = "8. Effects", col_names = TRUE,
                      na = c("","-")) %>%
  clean_names() %>% 
  rename("outcome_type" = outcome_type_10, "outcome_description" = outcome_type_11 )
#importamos la hoja 7. Evaluations el excel
evaluations <- read_excel(ruta_file, sheet = "7. Evaluations", col_names = TRUE) %>%
  clean_names() 
```

```{r}
effects %>%
  filter(outcome_type == 1) %>%
  distinct(evaluation_id)
```

# Correct type of variables

Select only required variables from evaluations sheet, and convert categorical variables to factor

```{r tame-evaluations}

evaluations_filter <- evaluations %>%
  select(paper_id, evaluation_id, 
         skills = ends_with("technical_soft_job_readiness"),
         training = ends_with("class_internship"), 
         jovenes,
         implementer,
         where_internship = starts_with("where_is_the_internship"),
         where_class = starts_with("where_is_the_classroom"),
         length_class_hours = ends_with("classroom_hours"),
         length_class_months = ends_with("classroom_months"),
         length_internship_hours = ends_with("internship_hours"),
         length_internship_months = ends_with("internship_months"),
         lac = ends_with("lac") ,
         decision=type_of_decision ,
         vulnerable=vulnerable_yes_no,
         vulnerability_type,
         holistic) %>%
  mutate_at(c("skills","training","where_internship","where_class",
              "jovenes","implementer"), 
            .fun = parse_factor, levels = NULL)

evaluations_filter <- evaluations_filter %>%
  mutate(implementer=recode(implementer, government="Government")) 

skim(evaluations_filter)

```

Select only required variables from effects sheet, and convert categorical variables to factor

```{r tame_effects}
effects_filter <- effects %>%
  select(paper_id, 
         evaluation_id:population,
         months_of_delay:outcome_description,
         n_total = n, nt:se,
         t,
         p_value,
         se_calculated, 
         starts_with("smd"),
         starts_with("vd")) %>%
  mutate(vd = if_else(is.na(vd_mean), vd_regress, vd_mean),
         gender = recode_factor(gender, Female = "female",
                                Pooled = "pooled", Male = "male") ) %>%
  select(-starts_with("vd_")) 

skim(effects_filter)
```
Somehow, `months_of_delay` is categorized as character, let's explore it:

```{r}
effects_filter %>% 
  filter(!is.na(months_of_delay)) %>%
  select(paper_id, months_of_delay) %>%
  mutate(months_numeric = as.numeric(months_of_delay)) %>%
  filter(is.na(months_numeric))
```
The problem is how Chakravarty 2016 ii and Dyke 2006 i coded its months of delay. Let's change it:

```{r}
effects_filter <- effects_filter %>%
  mutate(months_of_delay = replace(months_of_delay, months_of_delay == "9-11", 11),
         months_of_delay = replace(months_of_delay, months_of_delay == "0-4", 4),
         months_of_delay = as.numeric(months_of_delay)) 

effects_filter$months_of_delay %>% skim()


```

Now, we have outcomes reported between -6 to 156 months (13 years).


#Merge datasets (two sheets)
We merge the two previous datasets by paper_id and evaluation_id:

```{r join-frames}
effects_evaluations <- effects_filter %>%
  left_join(evaluations_filter, by= c("paper_id","evaluation_id"))

skim(effects_evaluations)
```
Since `age_group` contains information about the age of the group exposed to the effect
("22-30"), or is `NA` (when the effects is for the whole sample), we extract that information
to create four new variables, age_min and age_max for the age of the sample for the effect and
age_min_target and age_max_target for the evaluation.

effects_evaluations <- effects_evaluations %>%
  mutate(age_min = case_when(grepl("\\d\\d-\\d\\d",age_group) ~ substr(age_group,1,2),
                             grepl("\\d\\d-",age_group) ~ NA_character_,
                             grepl("\\d\\d+",age_group) ~ substr(age_group,1,2),
                             TRUE ~ NA_character_),
         age_max = case_when(grepl("\\d\\d-\\d\\d",age_group) ~ substr(age_group,4,5),
                             grepl("\\d\\d-",age_group) ~ substr(age_group,1,2),
                             grepl("\\d\\d+",age_group) ~ NA_character_,
                             TRUE ~ NA_character_),
         age_min_target = case_when(grepl("\\d\\d-\\d\\d",target_age) ~ substr(target_age,1,2),
                             grepl("\\d\\d-",target_age) ~ NA_character_,
                             grepl("\\d\\d+",target_age) ~ substr(target_age,1,2),
                             TRUE ~ NA_character_),
         age_max_target = case_when(grepl("\\d\\d-\\d\\d",target_age) ~ substr(target_age,4,5),
                             grepl("\\d\\d-",target_age) ~ substr(target_age,1,2),
                             grepl("\\d\\d+",target_age) ~ NA_character_,
                             TRUE ~ NA_character_)) %>%
  mutate_at(c("age_min_target", "age_max_target", "age_min", "age_max"), parse_number) %>%
  mutate(age_min = ifelse(is.na(age_group), age_min_target, age_min),
         age_max = ifelse(is.na(age_group), age_max_target, age_max))


effects_evaluations






Defining when an intervention is long or short depending on how many months in total there were


skim(effects_evaluations$length_internship_hours)
effects_evaluations <- effects_evaluations %>%
   rowwise()%>% 
   mutate(length_internship_hours = if_else(is.na(length_internship_hours), 
                                      length_internship_months*80, 
                                      length_internship_hours),
         length_class_hours =if_else(is.na(length_class_hours), 
                                    length_class_months*80, 
                                    length_class_hours),
        length_intervention= sum(length_internship_hours, length_class_hours, na.rm = TRUE))


median_length_intervention <- median(effects_evaluations$length_intervention)
median_length_intervention


median_length_interventrion_old <- effects_evaluations %>%
  filter(jovenes!="menor a 25") %>%
  pull(length_intervention) %>%
  median()

effects_evaluations <- effects_evaluations %>%
   mutate(length_intervention2=if_else(length_intervention<=median_length_intervention, 
                                      "Less or equal than 480 hours", "More than 480 hours"),
          length_intervention3=if_else(length_intervention<=median_length_interventrion_old, 
                                      "Less or equal than 400 hours", "More than 400 hours"))




Now, we create a histogram of how these intervention hours are distributed:


plot <- effects_evaluations %>%
  select(evaluation_id, length_intervention) %>%
  distinct() %>%
  ggplot(data = ., aes(length_intervention))+
  geom_histogram(binwidth = 200)+
  labs(title = "Distribution of intervention length", 
       x = "Hours", y = "Count")+
  theme_minimal()

plot 

ggsave(here("plots","distribution_of_intervention_length.png"), plot = plot)

effects_evaluations %>%
  select(evaluation_id,length_intervention2 ) %>%
  distinct() %>%
  count(length_intervention2)    


We modify categories, not including job-readiness since it is always part of 
technical o soft training.

```{r}

effects_evaluations <- effects_evaluations %>%
  mutate(skills= recode(skills,soft="Soft",technical="Technical",both="Both",
                        "technical, job-readniess"= "Technical",
                        "soft, job-readiness"= "Soft"),
         training=recode(training,both="Both",classroom="Classroom"),
         where_internship=recode(where_internship,"private-subsidized"="Private-subsidized",
                                 private="Private"),
         where_class=recode(where_class,public="Public",private="Private"),
         implementer=as.character(implementer),
        implementer=replace(implementer, implementer=="Multilateral","Mulilateral_NGO"),
        implementer=replace(implementer, implementer=="NGO","Mulilateral_NGO")) 

```

We perform a difference in means test to check whether there are statiscally significant
difference between men and women's sample sizes.

```{r}
t_test <- effects_evaluations %>% 
  filter(gender != "pooled" ) %>%
  t.test(formula = n_total ~ gender, data = .)

broom::tidy(t_test) %>%
  select(difference = estimate, female_mean_N = estimate1, 
         male_mean_N = estimate2, t = statistic,
         -parameter, conf.low:alternative) %>%
  write.xlsx(file = here("tables","t-test-gender.xlsx"))
```
Ordering for the forest plot subgroups
```{r}
effects_evaluations<-effects_evaluations %>%
  mutate(skills_order=recode(skills,Soft=1, Technical=2, Both=3),
         ) 
```


#Save file as RDS

Now, we save the file to be used in following steps

```{r}
saveRDS(effects_evaluations, file = here("data","cleanDatafile.rds"))
```


```{r}
effects_evaluations %>%
  filter(jovenes!="menor a 25",
         length_intervention == 480) %>%
  select(evaluation_id,starts_with("length")) %>%
  distinct()
  
effects_evaluations$outcome[effects_evaluations$outcome_type ==1 ] <- "Employment"
effects_evaluations$outcome[effects_evaluations$outcome_type ==3 ] <- "Formality"
effects_evaluations$outcome[effects_evaluations$outcome_type %in% c(2,8) ] <- "Wages all"
effects_evaluations$outcome[effects_evaluations$outcome_type %in% c(4,5,6,7) ] <- "Wages employed"

effects_evaluations%>%
  count(outcome, outcome_type)

effects_evaluations%>%
  filter(jovenes!="menor a 25") %>%
  count(outcome)

effects_evaluations%>%
  filter(jovenes!="menor a 25") %>%
  count()

hist(effects_evaluations$age_max_target)
skim(effects_evaluations$age_max_target)
```

