---
title: "R Notebook"
output: html_notebook
---

#Load libraries

```{r libraries, message=FALSE, warning=FALSE}
#install.packages(c("readxl","ggplot2","tidyverse","purrr","knitr","magrittr",
#"openxlsx","labelled","dplyr","here", "metafor"))
library(readxl)
library(tidyverse)
library(openxlsx)
library(dplyr)
library(here)
library(metafor)
library(skimr)
library(foreign)
source(file = here("coding-files","functions.R"))
```

#Load clean datafile

This file assumes that `0_data-cleaning.Rmd` has been previouly run to update rds file
in data folder.

```{r}
effects_evaluations <- readRDS(here("data","cleanDatafile.rds"))
  #filter(jovenes!="menor a 25")

effects_evaluations %>%
  filter(outcome_type == 1) %>%
  distinct(evaluation_id)
```

#Constructions of dataset with evaluations, effects and SE


## Are there estimates with gender == "pooled" but age_group != NA?
First, let's find out if there are estimates that are provided for `gender == "pooled"` but 
`age_group` is `NA`, that means that is for the whole sample.

```{r}
df1 <- effects_evaluations %>%
  filter(outcome_type == 1,
         is.na(age_group), 
         gender == "pooled") %>%
  select(1,2) %>%
  distinct()

df2 <- effects_evaluations %>%
  filter(outcome_type == 1,
         gender == "pooled") %>%
  select(1,2) %>%
  distinct()

anti_join(df2, df1, by = c("paper_id", "evaluation_id"))
anti_join(df1, df2, by = c("paper_id", "evaluation_id"))

rm(df1, df2)
```
```{r}
dfx<- effects_evaluations %>%
  filter(outcome_type == 1)
hist(dfx$beta)
```

All papers that have gender == "pooled" also provide an estimate for the whole sample in age. 

## Collapse evaluations with gender pooled and age pooled

Now, we add to a dataset the combined effect for evaluations that have one or more effects type 1. We only consider effects for `gender == "pooled"` and for the whole sample (`age_group == NA`)

To combine the effect accross different `months_of_delay`, we use the function 
`combineEffectsAcrossTime` with correlation equal to `0.5`.
```{r}
#ver como son los efectos a combinar en orden de tiempo
 employment_ver <- effects_evaluations %>%
  filter(outcome_type == 1,
         gender == "pooled",
         is.na(age_group)) %>%
  arrange(evaluation_id,paper_id, months_of_delay)
```

```{r}
employment_meta <- effects_evaluations %>%
  filter(outcome_type == 1,
         gender == "pooled",
         is.na(age_group)) %>%
  group_by(evaluation_id) %>%
  summarise(y = combineEffectsAcrossTime(y = beta, se = se_calculated)[1], 
            se = combineEffectsAcrossTime(y = beta, se = se_calculated)[2],
            number_effects = n())

employment_meta <- employment_meta %>% 
  mutate(gender = "pooled") %>%
  select(evaluation_id, gender, y:number_effects)

employment_meta
```


## Are there effects not reported for gender == "pooled" and is.na(age_group)
We want to find the effects that are reported separated for women and men, and not aggregated. Also, we want these  effects to be for the whole sample in regard to age (that is `age_group == NA`)

First, we find the effects without pool estimate

```{r papers-without-pool}
df1 <- effects_evaluations %>%
  filter(outcome_type == 1, gender == "pooled") %>%
  select(evaluation_id) %>%
  distinct()

df2 <- effects_evaluations %>%
  filter(outcome_type == 1, gender %in% c("male","female")) %>%
  select(evaluation_id) %>%
  distinct()

evaluation_female_or_male <- anti_join(df2,df1, by ="evaluation_id") 
evaluation_female_or_male

```

From this group of evaluations, we want to make sure that there are effects for the 
whole sample in regard to age:

```{r}
effects_gender_all_ages <- effects_evaluations %>%
  filter(outcome_type == 1, 
         evaluation_id %in% pull(evaluation_female_or_male),
         is.na(age_group)) %>%
  select(2) %>%
  distinct() 

anti_join(evaluation_female_or_male, effects_gender_all_ages, by="evaluation_id")

```

From this, there is a problematic paper (GAO 1996), that provides independent estimates
for males and females, and for different age ranges, not for the whole sample. 
We will deal with GAO separately.

## Collapsing by effects by gender and creating a pooled estimated

Now, we need to have only one estimate for each gender/paper_id/evaluation_id,

```{r}
effects_collapsed_by_gender <- effects_evaluations %>%
  filter(outcome_type == 1, 
         evaluation_id %in% pull(evaluation_female_or_male),
         is.na(age_group)) %>%
  group_by(evaluation_id, gender) %>%
  summarise(beta = combineEffectsAcrossTime(y = beta, se = se_calculated)[1], 
            se = combineEffectsAcrossTime(y = beta, se = se_calculated)[2],
            number_effects = n()) 

effects_collapsed_by_gender
```


```{r}
effects_evaluation_with_gender <- effects_collapsed_by_gender %>%
  group_by(evaluation_id) %>%
  mutate(y_pooled = combineEffectsGender(y = beta, se = se)[1], 
         se_pooled = combineEffectsGender(y = beta, se = se)[2],
         total_number_effects = sum(number_effects)) %>%
  ungroup() %>%
  mutate(gender_evaluation = ifelse(total_number_effects == number_effects, as.character(gender), "s.pooled"),
         gender_evaluation = parse_factor(gender_evaluation)) %>%
  select(-gender,-beta,-se) %>%
  distinct() %>%
  select(evaluation_id,
         gender = gender_evaluation,
         y = y_pooled, 
         se = se_pooled, 
         number_effects = total_number_effects ) 

effects_evaluation_with_gender
```

We combine with the previous table:

```{r}
employment_meta <- employment_meta %>% 
  bind_rows(effects_evaluation_with_gender) %>%
  mutate(gender = parse_factor(gender))

employment_meta
```

## Dealing with GAO 1996

Now, we deal with GAO 1996. First, we collapse by age_group and gender:


```{r}
gao_summary <- effects_evaluations %>%
  filter(evaluation_id == "GAO 1996",
         outcome_type == 1) %>%
  group_by(evaluation_id, gender, age_group) %>%
  summarise(beta_combined_delay = combineEffectsAcrossTime(beta, se_calculated)[1],
            se_combined_delay = combineEffectsAcrossTime(beta, se_calculated)[2],
            number_effects = n()) %>%
  group_by(evaluation_id) %>%
  summarise(y = combineEffectsGender(beta_combined_delay, se_combined_delay)[1],
            se = combineEffectsGender(beta_combined_delay, se_combined_delay)[2],
            number_effects = sum(number_effects))  %>%
  mutate( gender = "s.pooled") %>%
  select(1, gender, 2:4)

gao_summary

employment_meta <- employment_meta %>% 
  bind_rows(gao_summary) %>%
  mutate(gender = parse_factor(gender))

employment_meta
```



# Create DTA file to continue analysis in Stata

```{r}
employment_meta_categories <- employment_meta %>%
  left_join(
    effects_evaluations %>%
      select(
      evaluation_id,
      skills:where_class,
      #length_intervention2,
      #length_intervention3,
      #length_intervention,
      skills_order,
      lac,
      
      ) %>%
      distinct(),
  by = "evaluation_id"
  )
  
  employment_meta_categories
  
  write.dta(
    employment_meta_categories,
    file = here("data", "employment_meta_categories_v2.dta"),
    convert.factors = "string"
    )

```

## Create Scatter plot lenght intervention and employment


employment_meta_categories %>% 
  ggplot2::ggplot(data = ., aes(x = length_intervention, y = y)) +
  ggplot2::geom_point() +
  ggplot2::geom_vline(xintercept = 480) +
  labs(x = "Length of intervention (hours)", y = "Change of probability of employment") +
  ggplot2::theme_minimal()

ggplot2::ggsave(filename = here("plots", "scatter_length_intervention.pdf"))


# Meta-analysis


df2 <- employment_meta_categories %>% filter(implementer == "Government")  
count(df2)  
random_meta <- rma(yi = y, sei = se, data = employment_meta_categories, measure = "GEN",
                   slab = evaluation_id)
forest(random_meta, xlim = c(-0.8,0.5))
op <- par(cex = 0.75, font = 2)
text(-0.8, 36, "Evaluation ID", pos = 4)
text(0.2, 36, "Change in probability of employment", pos = 2)
text(0.5, 36, "[95% CI]", pos = 2)


